### 2020-01-30 wuhan.tex
bmb comments

\newcommand{\swp}[1]{\comment{magenta}{SWP}{#1}}
\newcommand{\jd}[1]{\comment{magenta}{JD}{#1}}
\newcommand{\new}[1]{\textcolor{blue}{#1}}

@@

>>>>

\newcommand{\swp}[1]{\comment{magenta}{SWP}{#1}}
\newcommand{\jd}[1]{\comment{magenta}{JD}{#1}}
\newcommand{\bmb}[1]{\comment{magenta}{BMB}{#1}}
\newcommand{\new}[1]{\textcolor{blue}{#1}}

@@

\bmb{general comments (Daniel may have taken notes on these already):
  \begin{itemize}
  \item try flatter-at-origin priors (e.g. half-Cauchy)?
  \item Stan implementation?
  \item comment on broader uncertainty context (King/Rohani on observation + process error, major reporting irregularities, non-stationarity \ldots)
  \item cite Elderd et al on point estimates??
  \item colorspace package ({\tt scale\_colour\_discrete\_qualitative} or other) for Figure 3?
  \end{itemize}
}
